Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-12 paper/disc20clustering.tex
The right insigths into generalizing LB

First, we construct a ground set of size $k-1$ on an arbitrarily chosen cluster.
In any partition, there must exist an isolated node collocated with the ground set of size $k-1$.
We issue requests between this isolated node, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, we show that there exists an optimal offline algorithm \OPT that performs only two migrations.
Figure~\ref{fig:lb} illustrates the constructs used in the lower bound.

>>>>

First, we construct a ground set of size $k-1$ on an arbitrarily chosen cluster.
In any partition, there must exist an isolated node collocated with the ground set of size $k-1$, and we call it \emph{special}.
We issue requests between the current special node, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, we show that there exists an optimal offline algorithm \OPT that performs only two migrations.
Figure~\ref{fig:lb} illustrates the constructs used in the lower bound.
